---
title: "AM10 Individual Assignment"
author: "Mingqi Yin"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
---

```{r, setup, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy = FALSE,     # display code as typed
  size = "small")   # slightly smaller font for code
options(digits = 3)


```

```{r libraries, include=FALSE}
library(tidyverse) # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(vroom)
library(ggtext)
library(ggrepel)
library(patchwork)
library(gghighlight)
library(remotes)
library(ggdogs)
library(lubridate)
library(forcats)
library(GGally)
library(readxl)
library(here)
library(skimr)
library(janitor)
library(broom)
library(tidyquant)
library(infer)
library(openintro)
library(readr)

library(tidyverse)
library(vroom)
library(extrafont)
library(ggtext)

loadfonts(device="win")
```

*Please note that my graphs don't display properly in this html, hence I have included the png files in the assignment too. Sorry for the inconvinience.*

# Question 1: Grading JP Morgan Visualisation

Text:

-   6-12 descriptive title: 2

-   Subtitle providing additional information: 2

-   Text size readable: 2

-   Text horizontal: 2

-   Data labelled directly: 1 (not labelled directly)

-   Labels used sparingly: 1 (crammed)

Arrangement:

-   Accurate proportions: 2

-   Intentionally ordered: 0 (no visible ordering)

-   Axis intervals are equidistant: 2

-   Graph is 2D: 2

-   Display is free from decoration: 2

Colour:

-   Colour scheme is intentional: 0 (no visible intentions in colour scheme)

-   Colour used to highlight key patterns: 0 (no highlighting of key patterns)

-   Colour is legible when printed in black and white: 0 (not legible)

-   Colour is legible for people with colour-blindness: 0 (not legible)

-   Text sufficiently contrasts background: 2

Lines:

-   Gridlines are muted: 2

-   Graph does not have border line: 2

-   Axes do not have unnecessary tick marks or axis lines: 2

-   Graph has one horizontal and one vertical axis: 2

Overall:

-   Graph highlights significant finding or conclusion: 2

-   Type of graph is appropriate for data: 2

-   Graph has appropriate level of precision: 1 (may be too precise)

-   Individual chart elements work together to reinforce the overarching takeaway: 1 (too many lines to illustrate the same idea)

Total:

-   34/48 = 70.83%

# Question 2 - Ugly Graph

```{r, bad_graph}

# read data
atheism <- read_csv("atheism copy.csv")

# create binary variable for whether atheism
atheism <- atheism %>%
  mutate(binary = ifelse(test = response == "non-atheist",
                         yes = 0,
                         no = 1))

# produce summary table
sum_atheism <- atheism %>%
  group_by(nationality, year, binary) %>%
  summarise(count = n())

# plot diagram
ggplot(data = sum_atheism,
       aes(x = binary, y = count, colour = nationality)) + # binary not being a factor variable
  geom_dog(dog = "husky_2", size = 17) + 
  facet_wrap(~nationality) + # making it messy
  labs(title = "aTHeist Or noT", # doesn't make sense
       x = "atheist or not",
       y = "number") +
  theme_dark() # make it messy

```

# Question 3 - Stop and Search

```{r, stop_and_search_dataset}

# read and clean
stop_and_search <- read_csv("stop_and_search.csv") %>%
  janitor::clean_names()

stop_and_search <- stop_and_search %>%
  mutate(date = as.character(date))

# unique(dataframe$variable) unique values in variables to check
stop_and_search_clean <- stop_and_search %>%
  select(-policing_operation, -self_defined_ethnicity, -outcome_linked_to_object_of_search, -removal_of_more_than_just_outer_clothing, -date, -legislation, -part_of_a_policing_operation, -latitude, -longitude)

# variables of interest
# type: person, vehicle, person and vehicle
# gender: female, male, other, NA
# age_range: under 10, 10-17, 18-24, 25-34, over 34
# officer_identified_race: White, Black, Asian, Other, NA
# object_of_search: Controlled drugs, Offensive weapons, Stolen goods, Articles for use in criminal damage, Evidence of offences under the Act, Firearms, Anything to threaten or harm anyone, Fireworks, NA
# outcome: A no further action disposal, Arrest, Penalty Notice for Disorder, Community resolution, Summons / charged by post, Caution (simple or conditional)

# searches dataset for plot 1
searches <- stop_and_search_clean %>%
  select(type, officer_defined_ethnicity, object_of_search, outcome) %>%
  filter(outcome == "Arrest" & type %in% c("Person search", "Person and Vehicle search")) %>%
  rename(race = officer_defined_ethnicity) %>%
  drop_na() %>%
  group_by(race, type) %>%
  summarise(count = n())

# arrested dataset for plot 2
arrested <- stop_and_search_clean %>%
  select(-type) %>%
  filter(outcome == "Arrest") %>%
  rename(race = officer_defined_ethnicity) %>%
  drop_na() %>%
  group_by(object_of_search, age_range) %>%
  summarise(count = n())

# arrested pivot to wide to find percentages and then pivot back to long
arrested_wider <- arrested %>%
  pivot_wider(names_from = "age_range",
              values_from = "count") %>%
  janitor::clean_names() %>%
  rename(aged_18_24 = x18_24,
         aged_10_17 = x10_17,
         aged_25_34 = x25_34,
         aged_over_34 = over_34) %>%
  select(aged_10_17, aged_18_24, aged_25_34, aged_over_34) %>%
  drop_na() %>%
  mutate(sum = aged_10_17 + aged_18_24 + aged_25_34 + aged_over_34) %>%
  mutate(aged_10_17 = aged_10_17 / sum,
         aged_18_24 = aged_18_24 / sum,
         aged_25_34 = aged_25_34 / sum,
         aged_over_34 = aged_over_34 / sum) %>%
  select(-sum) %>%
  pivot_longer(cols = 2:5,
               names_to = "age",
               values_to = "percentage")
 
  

```

```{r, plot_1, fig.width = 7, fig.height = 7}
ggplot(data = searches,
       aes(x = fct_reorder(race, count, sum, .desc = TRUE), y = count, fill = type)) +
  geom_col(width = 0.5, position = position_dodge()) +
  labs(title = "More white people are arrested following stop and searches",
       subtitle = "But more black people proportional to the population are arrested following stop and searches", 
       x = "Race",
       y = "Number of individuals") +
  theme_minimal() +
  theme(plot.subtitle = element_text(size = 20, face = 'italic', colour = 'red'),
        plot.title = element_text(size = 25, face = 'bold', colour = 'black'),
        aspect.ratio = 1,
        plot.title.position = "plot",
        axis.text = element_text(size = 18),
        axis.title.y = element_blank(),
        axis.title.x = element_text(size = 20),
        legend.text = element_text(size = 18),
        legend.title = element_blank(),
        legend.position = "bottom")

```

```{r, plot_2, fig.width = 15, fig.height = 10}

ggplot(data = arrested_wider,
       aes(x = object_of_search, y = percentage, fill = age)) +
  geom_col() +
  scale_fill_brewer(palette = "Blues") +
  theme_minimal() +
  labs(title = "Over 34 y/os make up of the highest percentage of most crimes committed",
       x = "Object of search") +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal() +
  theme(plot.title = element_text(size = 50, face = 'bold', colour = 'blue', hjust = 0.5),
        axis.text = element_text(size = 22),
        axis.title.y = element_blank(),
        axis.title.x = element_text(size = 30),
        legend.text = element_text(size = 30),
        legend.title = element_blank())

```
